Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Update paper.qmd
Further explained data section and updated the abstract.

---
title: "Forecasting the 2024 U.S. Presidential Election"
subtitle: "Using Aggregated Polling Data to Predict the Outcome of the 2024 Presidential Race"
author: 
  - Andy Jiang
  - Onon Burentuvshin
  - Rui Hu
thanks: "Code and data are available at: [https://github.com/AndyYanxunJiang/president-polls)."
date: today
date-format: long
abstract: "The 2024 U.S. presidential election is shaping up to be a highly swing race, with polling data playing a crucial role in gauging public sentiment and forecasting the potential outcome. This paper aims to build a predictive model using a poll-of-polls approach, aggregating data from multiple pollsters to forecast the winner of the upcoming election. The analysis incorporates polling data from various sources, filtered to include only high-quality pollsters with a numeric grade above 3, to ensure the reliability of the predictions. Additionally, a detailed examination of one selected pollster’s methodology is conducted, highlighting strengths, weaknesses, and biases in the survey process. The paper concludes with an idealized polling methodology, designed within a $100K budget, to enhance the accuracy of election forecasts. Results are presented in the context of understanding polling trends, potential biases, and the evolving landscape of voter preferences as the election approaches."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

This paper aims to forecast the outcome of the 2024 U.S. presidential election by leveraging a "poll-of-polls" approach, which aggregates data from various pollsters to create a more comprehensive picture of the race. By focusing on high-quality polls and conducting a detailed analysis of the polling trends for the two main candidates, Donald Trump and Kamala Harris, we seek to uncover patterns in voter support and potential factors influencing shifts in public opinion. Additionally, the paper examines the methodologies of different pollsters to assess their strengths and weaknesses, which can help identify possible biases in the aggregated data.

The analysis will further explore the geographic distribution of support across key swing states, providing insights into the electoral landscape. Finally, the paper presents an idealized polling methodology with a $100,000 budget, designed to improve the accuracy and representativeness of election forecasts. By integrating multiple data sources and critically evaluating polling practices, this study aims to contribute to the ongoing discussion on the role of polling in democratic processes and election forecasting.

>>>>

---
title: "Forecasting the 2024 U.S. Presidential Election"
subtitle: "Using Aggregated Polling Data to Predict the Outcome of the 2024 Presidential Race"
author: 
  - Andy Jiang
  - Onon Burentuvshin
  - Rui Hu
thanks: "Code and data are available at: [https://github.com/AndyYanxunJiang/president-polls)."
date: today
date-format: long
abstract: "The 2024 U.S. presidential election is shaping up to be a highly swing race, with polling data playing a crucial role in gauging public sentiment and forecasting the potential outcome. This paper builds a predictive model using a poll-of-polls approach, aggregating data from multiple pollsters to forecast the winner of the upcoming election. The analysis incorporates polling data from various sources, filtered to include only high-quality pollsters with a numeric grade above 3, to ensure the reliability of the predictions. By incorporating the poll-of-polls approach with our model, we predict that Kamla Harris edges our Trump in the presidential election. Our model forecasts that with a 1%-4% margin lead in Pennsylvania, Wisconsin, Nevada, and Michigan, Kamala Harris will accumulate 276 electoral votes to win the election. Additionally, a detailed examination of one selected pollster’s methodology is conducted, highlighting strengths, weaknesses, and biases in the survey process. The paper concludes with an idealized polling methodology, designed within a $100K budget, to enhance the accuracy of election forecasts. Results are presented in the context of understanding polling trends, potential biases, and the evolving landscape of voter preferences as the election approaches."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

This paper aims to forecast the outcome of the 2024 U.S. presidential election by leveraging a "poll-of-polls" approach, which aggregates data from various pollsters to create a more comprehensive picture of the race. Poll-of-polls approach allows us to access a wide breatdth of data that mitigates potential biases and errors committed by any single pollster. By focusing on high-quality polls and conducting a detailed analysis of the polling trends for the two main candidates, Donald Trump and Kamala Harris, we seek to uncover patterns in voter support and potential factors influencing shifts in public opinion. Additionally, the paper examines the methodologies of different pollsters to assess their strengths and weaknesses, which can help identify possible biases in the aggregated data.

The analysis will further explore the geographic distribution of support across key swing states, providing insights into the electoral landscape. Thus, our estimand will be the share of voter support for each presidential candidate in each swing state. Finally, the paper presents an idealized polling methodology with a $100,000 budget, designed to improve the accuracy and representativeness of election forecasts. By integrating multiple data sources and critically evaluating polling practices, this study aims to contribute to the ongoing discussion on the role of polling in democratic processes and election forecasting.
